Provenance analysis

### 2021-08-09 analysis/provenance2.Rmd
Parse from file number
Addin the external line

@@

@@

@@

>>>>

external_calls <- E_prov %>% filter(provenance == ".External")

@@

external_sites <- external_calls %>% pull(src_ref) %>% n_distinct()

@@

r("nb external sites", external_sites)
r("external sites percent", ratio(symbol_sites, nb_call_sites))

@@

## Parse from a file

```{r parse_from_file}

parsed_from_file_calls <- string_calls %>% filter(str_detect(provenance_args, "\\bfile\\b"))

parsed_from_file_sites <- parsed_from_file_calls %>% pull(src_ref) %>% n_distinct()

r("nb parse from file sites", parsed_from_file_sites)
